Build Your Own EV: A Rapid Energy-Aware Synthesis of Electric Vehicles

### 2018-07-30 draft/draft_nograph.tex
Check word count

%\begin{figure}
%\centering
%\includegraphics[width=1.0\hsize]{Figures/source_of_electricity.pdf}
%\caption{(a) The source of electricity in the United States and (b) annual $\rm CO_2$ emission by vehicle type~\cite{AFDC}.}
%\label{fig:sources}
%\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\hsize]{Figures/fuel_efficiency.pdf}
\caption{Fuel efficiency of vehicles by curb weight: (a) all passenger vehicles and (b) electric vehicles only.}
\label{fig:fuel_efficiency}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=1.0\hsize]{Figures/Campus_route.pdf}
\caption{(a) A campus mail delivery route, (b) road elevation change and driving cycle and (c) example electric vehicle setups and energy consumption comparison.}
\label{fig:example_route}
\end{figure}

%\begin{figure}
%\centering
%\includegraphics[width=1.0\hsize]{Figures/Campus_example_results.pdf}
%\caption{Example electric vehicle setups and energy consumption comparison.}
%\label{fig:example_results}
%\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=1.0\hsize]{Figures/Framework_existing.pdf}
\caption{Existing electric vehicle design-time optimization dedicated to a driving mission.}
\label{fig:framework_existing}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.7\hsize]{Figures/GUI.pdf}
\caption{An example of graphical user interface of the rapid energy-aware electric vehicle synthesis.}
\label{fig:GUI}
\end{figure}

@@

%\begin{figure}
%\centering
%\includegraphics[width=1.0\hsize]{Figures/Framework_GUI.pdf}
%\caption{A diagram of the rapid energy-aware electric vehicle synthesis operation flow for user preferences and a driving mission.}
%\label{fig:framework_GUI}
%\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=1.0\hsize]{Figures/E_generic.pdf}
\caption{Energy consumption per curb weight by the motor power rating and gearbox ratio.}
\label{fig:E_generic}
\end{figure}

@@

%\begin{figure}
%\centering
%\includegraphics[width=1.0\hsize]{Figures/UCR_driving_plan.pdf}
%\caption{Road elevation change and driving cycle (velocity over time) (a) from home to work and (b) from work to home.}
%\label{fig:UCR_driving_plan}
%\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=1.0\hsize]{Figures/Framework_proposed.pdf}
\caption{A diagram of the rapid energy-aware electric vehicle synthesis flow dedicated to a driving mission.}
\label{fig:framework_proposed}
\end{figure}

\begin{figure*}
\centering
\includegraphics[width=0.9\hsize]{Figures/synthesis_results.pdf}
\caption{Results of the rapid energy-aware electric vehicle synthesis dedicated for a driving mission.}
\label{fig:synthesis_results}
\end{figure*}

@@

%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{testing.pdf}}]{Donkyu Baek}
%Biography text here.
%\end{IEEEbiography}
%
%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{testing.pdf}}]{Hyung Gyu Lee}
%Biography text here.
%\end{IEEEbiography}
%
%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{testing.pdf}}]{Naehyuck Chang}
%Biography text here.
%\end{IEEEbiography}

>>>>

%\begin{figure}
%\centering
%%\includegraphics[width=1.0\hsize]{Figures/source_of_electricity.pdf}
%%\caption{(a) The source of electricity in the United States and (b) annual $\rm CO_2$ emission by vehicle type~\cite{AFDC}.}
%\label{fig:sources}
%\end{figure}

@@

\begin{figure}
\centering
%\includegraphics[width=0.9\hsize]{Figures/fuel_efficiency.pdf}
%\caption{Fuel efficiency of vehicles by curb weight: (a) all passenger vehicles and (b) electric vehicles only.}
\label{fig:fuel_efficiency}
\end{figure}

@@

\begin{figure}
\centering
%\includegraphics[width=1.0\hsize]{Figures/Campus_route.pdf}
%\caption{(a) A campus mail delivery route, (b) road elevation change and driving cycle and (c) example electric vehicle setups and energy consumption comparison.}
\label{fig:example_route}
\end{figure}

%\begin{figure}
%\centering
%%\includegraphics[width=1.0\hsize]{Figures/Campus_example_results.pdf}
%%\caption{Example electric vehicle setups and energy consumption comparison.}
%\label{fig:example_results}
%\end{figure}

@@

\begin{figure}
\centering
%\includegraphics[width=1.0\hsize]{Figures/Framework_existing.pdf}
%\caption{Existing electric vehicle design-time optimization dedicated to a driving mission.}
\label{fig:framework_existing}
\end{figure}

@@

\begin{figure}
\centering
%\includegraphics[width=0.7\hsize]{Figures/GUI.pdf}
%\caption{An example of graphical user interface of the rapid energy-aware electric vehicle synthesis.}
\label{fig:GUI}
\end{figure}

@@

%\begin{figure}
%\centering
%%\includegraphics[width=1.0\hsize]{Figures/Framework_GUI.pdf}
%%\caption{A diagram of the rapid energy-aware electric vehicle synthesis operation flow for user preferences and a driving mission.}
%\label{fig:framework_GUI}
%\end{figure}

@@

\begin{figure}
\centering
%\includegraphics[width=1.0\hsize]{Figures/E_generic.pdf}
%\caption{Energy consumption per curb weight by the motor power rating and gearbox ratio.}
\label{fig:E_generic}
\end{figure}

@@

%\begin{figure}
%\centering
%%\includegraphics[width=1.0\hsize]{Figures/UCR_driving_plan.pdf}
%%\caption{Road elevation change and driving cycle (velocity over time) (a) from home to work and (b) from work to home.}
%\label{fig:UCR_driving_plan}
%\end{figure}

@@

\begin{figure}
\centering
%\includegraphics[width=1.0\hsize]{Figures/Framework_proposed.pdf}
%\caption{A diagram of the rapid energy-aware electric vehicle synthesis flow dedicated to a driving mission.}
\label{fig:framework_proposed}
\end{figure}

\begin{figure*}
\centering
%\includegraphics[width=0.9\hsize]{Figures/synthesis_results.pdf}
%\caption{Results of the rapid energy-aware electric vehicle synthesis dedicated for a driving mission.}
\label{fig:synthesis_results}
\end{figure*}

@@

%\begin{IEEEbiography}[{%\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{testing.pdf}}]{Donkyu Baek}
%Biography text here.
%\end{IEEEbiography}
%
%\begin{IEEEbiography}[{%\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{testing.pdf}}]{Hyung Gyu Lee}
%Biography text here.
%\end{IEEEbiography}
%
%\begin{IEEEbiography}[{%\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{testing.pdf}}]{Naehyuck Chang}
%Biography text here.
%\end{IEEEbiography}
